\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphics}
\usepackage{libertine}

\begin{document}

link : https://labs.spotify.com/2014/09/16/squad-health-check-model/

\section{First slide}

\subsection{Squad Health Check model}

version 1, September 2014

\subsubsection{What is this?}

\begin{itemize}
\item A workshop \& visualization technique for helping squads* improve
\end{itemize}

\subsubsection{Who is it for?}

\begin{itemize}
\item The squad itself
\item People supporting the squad (managers, coaches, etc)
\end{itemize}

\subsubsection{How to use the model}

\begin{itemize}
\item Print the cards \& laminate


\begin{itemize}
\item Slide 2-5 = Awesome Cards (double sided)
\item Slide 6-9 = Voting cards (double sided)
\end{itemize}
\item Get the squad together in a room
\item Discuss the Awesome Cards. Each one is a health indicator with an “example of awesome”, and an “example of crappy”.
\item Ask the squad how they feel about each health indicator, using techniques such as voting cards.


\begin{itemize}
\item Green doesn’t mean Perfect. It just means the squad is happy with this, and see no major need for improvement right now.
\item Yellow means there are some important problems that need addressing, but it’s not a disaster.
\item Red means this really sucks and needs to be improved.
\end{itemize}
\item Also discuss the trends (are things improving, stable, or getting worse?)
\item Visualize the result, for example like this:
\item Use the data to help the squad(s) improve
\end{itemize}

\subsubsection{Tips}

\begin{itemize}
\item These cards are just a starting point. Squad is free to add/remove/tweak the questions to match what they think matters.
\item Make sure this is used to support the squads, not judge them!
\end{itemize}

Squad is Spotify’s term for a small, cross-functional, self-organizing development team

\section{Second slide}

\subsection{Delivering Value}

\begin{itemize}
\item We deliver great stuff! We're proud of it and our stakeholders are really happy.
\item We deliver crap. We feel ashamed to deliver it. Our stakeholders hate us.
\end{itemize}

\subsection{Easy to release}

\begin{itemize}
\item Releasing is simple, safe, painless and mostly automated.
\item Releasing is risky, painful, lots of manual work and takes forever.
\end{itemize}

\subsection{Fun}

\begin{itemize}
\item We love going to work and have great fun working together!
\item Boooooooring\ldots{}
\end{itemize}

\subsection{Health of Codebase}

\begin{itemize}
\item We're proud of the quality of our code! It is clean, easy to read and has great test coverage.
\item Our code is a pile of dung and technical debt is raging out of control.
\end{itemize}

\subsection{Learning}

\begin{itemize}
\item We're learning lots of interesting stuff all the time!
\item We never have time to learn anything.
\end{itemize}

\subsection{Mission}

\begin{itemize}
\item We know exactly why we are here and we’re really excited about it!
\item We have no idea why we are here, there's no high lever picture or focus. Our so called mission is completely unclear and uninspiring.
\end{itemize}

\subsection{Pawns or Players}

\begin{itemize}
\item We are in control of our own destiny! We decide what to build and how to build it.
\item We are just pawns in a game of chess with no influence over what we build or how we build it.
\end{itemize}

\subsection{Speed}

\begin{itemize}
\item We get stuff done really quickly! No waiting and no delays.
\item We never seem to get anything done. We keep getting stuck or interrupted. Stories keep getting stuck on dependencies.
\end{itemize}

\section{Third slide}

\subsection{Suitable Process}

\begin{itemize}
\item Our way of working fits us perfectly!
\item Our way of working sucks!
\end{itemize}

\subsection{Support}

\begin{itemize}
\item We always get great support and help when we ask for it!
\item We keep getting stuck because we can't get the support and help that we ask for.
\end{itemize}

\subsection{Teamwork}

\begin{itemize}
\item We are a totally gelled super-team with awesome collaboration!
\item We are a bunch of individuals that neither know nor care about what the other people in the squad are doing.
\end{itemize}

\end{document}
